Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training and Inference with GPUs

### 2020-12-26 NEUROC/sec4-experiments.tex
更新后几章

However, the overheads brought by sampling and data transferring from CPU to GPU became obvious when the batch size was small.
%
Figure~\ref{fig:time_breakdown_of_inference_sampler} shows the time breakdowns of sample-based inference on different datasets.
%
On the \texttt{amp} and \texttt{cam} datasets, the sampling time even accounted for near half of the total inference time.
%
The results indicated that the current implementation of inference sampler in PyG was also inefficient.
%
Improving its efficiency could significantly reduce the sample-based inference time.

@@

\paragraph{Summary of Sampling Techniques}
% 
The sampled subgraphs produced by the neighbor sampler and the cluster sampler had lower average degrees than the original graph.
%
With small batch sizes, the sampling techniques could significantly reduce the training/inference time per batch and the peak memory usage.
%
However, the batch size should be small to limit the memory usage, especially for inference.
%
The current implementation of the sampling techniques in PyG was inefficient to handle small batches.
%
Small batches could not make full use of the computing power of a GPU.
%
The time spent on the sampling phase and the data transferring phase could even exceed the training/inference phase.

>>>>

However, the overheads brought by sampling and data transferring from CPU to GPU became obvious when the batch size was small.
%
Figure~\ref{fig:time_breakdown_of_inference_sampler} shows the time breakdowns of sample-based inference on different datasets.
%
The 
%
On the \texttt{amp} and \texttt{cam} datasets, the sampling time even accounted for near half of the total inference time.
%
The results indicated that the current implementation of inference sampler in PyG was also inefficient.
%
Improving its efficiency could significantly reduce the sample-based inference time.

@@

\paragraph{Summary of Sampling Techniques}
% 
The sampled subgraphs produced by the neighbor sampler and the cluster sampler had lower average degrees than the original graph.
%
With small batch sizes, the sampling techniques could significantly reduce the peak memory usage per batch.
%
However, the current implementation of the sampling techniques in PyG was inefficient to handle small batches.
%
The time spent on the sampling phase and the data transferring phase could even exceed the training/inference phase.
%
Small batches could not make full use of the computing power of a GPU either.

### 2020-12-26 NEUROC/sec7-conclusion.tex
更新后几章

In this work, we systematically explore the performance bottlenecks in graph neural network training and inference. 
We model the existing GNNs with the message-passing framework. 
We classify the GNNs according to their edge and vertex calculation complexity to select four typical GNNs for evaluation. 
The experimental results validate our complexity analysis. Fixing other hyper-parameters, the training time and the memory usage increase linearly with each hyper-parameter of the four GNNs. 
To find out the performance bottleneck in the training/inference time, we decompose the training/inference time per epoch on different levels. 
The time breakdown analysis indicates that the edge calculation stage and its related basic operators are the performance bottleneck for most GNNs. 
Moreover, the intermediate results produced by the edge calculation stage cause high memory usage, limiting the data scalability. 
Adopting sampling techniques can reduce the training time and the memory usage significantly. 
However, the current implementation of the sampling techniques in PyG brings considerable sampling overheads. 
The small sampled subgraphs cannot make full use of the computing power of a GPU card either. 
Our analysis indicates that the edge calculation stage should be the main target of optimizations. 
Reducing its memory usage and improving its efficiency can significantly improve the performance of the GNN training and inference. 
Based on the analysis, we propose several potential optimizations for the GNN frameworks. 
We believe that our analysis can help developers to have a better understanding of the characteristics of GNN training and inference.

>>>>

In this work, we systematically explore the performance bottlenecks in graph neural network training and inference.
%
We model the existing GNNs with the message-passing framework. 
%
We classify the GNNs according to their edge and vertex calculation complexity to select four typical GNNs for evaluation. 
%
The experimental results validate our complexity analysis.
%
Fixing other hyper-parameters, the training time, inference time and memory usage increase linearly with each hyper-parameter of the four GNNs.
%
To find out the performance bottlenecks in the training/inference time, we decompose the training/inference time per epoch on different levels.
%
The time breakdown analysis indicates that the edge calculation stage and its related basic operators are the performance bottlenecks for most GNNs.
%
Moreover, the intermediate results produced by the edge calculation stage cause high memory usage, limiting the data scalability.
%
Adopting sampling techniques can reduce the memory usage of training and inference significantly.
%
However, the current implementation of the sampling techniques in PyG brings considerable sampling overheads.
%
The small sampled subgraphs cannot make full use of the computing power of a GPU card either.
% 
Our analysis indicates that the edge calculation stage should be the main target of optimizations.
%
Reducing its memory usage and improving its efficiency can significantly improve the performance of GNN training and inference.
%
Based on the analysis, we propose several potential optimizations for the GNN libraries/systems.
%
We believe that our analysis can help developers to have a better understanding of the characteristics of GNN training and inference.
